%-------------------------
% Resume in Latex
% Author : Jagadish R
% License : MIT
%------------------------
\documentclass[11pt]{extarticle}
\usepackage[colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=blue,pdftitle={Jagadish R - Resume},pdfpagemode=FullScreen]{hyperref}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{-2.1pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jagadish R} 
  
  \\ \faEnvelope\href{mailto:jagadishr6300@gmail.com}{: jagadishr6300@gmail.com} &
  
 \faGithub \href{https://github.com/jagadish-ravichandran}{: github.com/jagadish-ravichandran}
  \\
 \faMobile : +91 9597867439  &
   \faLinkedin \href{https://www.linkedin.com/in/jagadish-r-b4822b216/}{: linkedin.com/jagadish-r}

\end{tabular*}

%-----------Summary----------------
\section{Summary}
   \hspace{5mm} Software Engineer focused on delivering resilient, maintainable, and business-aligned software solutions. Experienced in designing domain-driven backend systems, balancing engineering quality, technical trade-offs, and delivery timelines to support reliable software releases. Passionate about understanding business domains and building scalable products that solve real-world problems.

%-----------EDUCATION----------------
\section{Education}
\vspace{2mm}
  \resumeSubHeadingListStart
   \resumeSubheading
      {SSN College Of Engineering}{Chennai}
      {BE in Computer Science and Engineering; GPA: 8.38}{Aug 2019 - Jun 2023}
      
  \resumeSubHeadingListEnd


%-----------SKILLS-----------------
\section{Skills \& Competencies}
\vspace{3mm}
  \resumeSubHeadingListStart
  \resumeSubItem{Languages: }
      {Java, Python, SQL, JavaScript, Bash, C}
      \resumeSubItem{Frameworks \& Technologies: }
      {Spring Boot, Spring Security, Spring Data JPA, React.js, Node.js, Django, Flask, GraphQL}
      \resumeSubItem{Databases \& Storage: }
      {PostgreSQL, MongoDB, MinIO}
      \resumeSubItem{Cloud \& DevOps: }
      {Docker, GitHub Actions, Jenkins, DigitalOcean, CI/CD, GitFlow}
      \resumeSubItem{Testing \& Quality: }
      {JUnit, Cucumber, Testcontainers, WireMock, SonarCloud}
      \resumeSubItem{AI-Assisted Development: }
      {Spec-driven development, spec-to-code workflows, AI-assisted engineering (Claude Code/Web/Skills), MCP integrations with GitHub \& Jira, human-in-the-loop review process}

 \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Axelate Solutions — Software Engineer} & \textit{\small Hybrid | Jun 2025 - Jun 2026} \\
  \end{tabular*}\vspace{-5pt}

 \resumeItemListStart
        \item{Developed domain-driven backend services for a multi-tenant B2B SaaS platform using Java 21 and Spring Boot, implementing rich domain models while keeping business logic independent from application and infrastructure concerns.}
        \item{Owned database schema evolution using PostgreSQL and Liquibase, ensuring data integrity, backward compatibility, and seamless production deployments.}
        \item{Developed tenant-aware security capabilities, integrating JWT, OTP, and DPoP authentication while enforcing domain-level and database-level tenant isolation.}
        \item{Led the delivery of integrations with external business platforms, working closely with stakeholders and third-party vendors to interpret requirements, navigate ambiguous API documentation, resolve production issues, and implement reliable solutions supporting critical business operations.}
        \item{Established high engineering quality standards through behavior-driven testing, Testcontainers, WireMock, SonarCloud quality gates, and end-to-end observability.}
        \item{Implemented CI/CD pipelines and cloud deployments using GitHub Actions, GitFlow, and DigitalOcean, utilizing App Platform, Container Registry, Managed PostgreSQL, and S3-compatible object storage to support reliable and scalable application delivery.}
      \resumeItemListEnd

\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Crayon Data — Associate Software Engineer} & \textit{\small Hybrid | Aug 2023 - Jun 2025} \\
  \end{tabular*}\vspace{-5pt}

 \resumeItemListStart
        \item{Developed GraphQL APIs using Hasura for a configuration-driven mobile application, enabling flexible and efficient data retrieval.}
        \item{Built an automated email notification service in Spring Boot with retry mechanisms to improve reliability and fault tolerance.}
        \item{Enhanced backend performance and security for a digital banking platform through database optimization, PL/SQL development, and code obfuscation techniques.}
      \resumeItemListEnd

\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Inoesis Technologies — Software Developer Intern} & \textit{\small Remote | Aug 2021 - Feb 2022} \\
  \end{tabular*}\vspace{-5pt}

 \resumeItemListStart
        \item{Implemented Django-based REST APIs and integrated Twilio Video APIs for teleconsultation and appointment management features in healthcare applications.}
      \resumeItemListEnd
       
 \resumeSubHeadingListEnd
 
 
 %-----------AI-NATIVE DEVELOPMENT-----------------
\section{AI-Native Software Development Practices}
\vspace{2mm}
\resumeSubHeadingListStart

\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{AI-Augmented Development Workflow} & \textit{\small 2025 - 2026} \\
  \end{tabular*}\vspace{-5pt}

 \resumeItemListStart
        \item{Applied spec-driven development workflows to transform product requirements into implementation plans, test cases, and deliverable software.}
        \item{Leveraged Claude Code, Claude Web, and Claude Skills for AI-assisted design, implementation, refactoring, and engineering automation.}
        \item{Integrated MCP tools with GitHub and Jira to enable context-aware development across code, issues, and pull requests.}
        \item{Established a human-in-the-loop review process to validate AI-generated plans, code, and architectural decisions before delivery.}
      \resumeItemListEnd
 
 \resumeSubHeadingListEnd
 
 
 % -----------PROJECTS-----------------
\section{Projects}
\vspace{2mm}
      \href{https://personal-expense-management-app.onrender.com}{\textbf{Personal Expense Tracker}} — Expense tracking app built with Flask and PostgreSQL featuring a category-based dashboard, monthly breakdowns, and CI/CD on Vercel. \hfill \textbf{2022}
      
      \vspace{2mm}
      \href{https://telegram.me/formspot_bot}{\textbf{Form Bot}} — Built a form automation platform leveraging Python, Telegram Bot API, and PostgreSQL for creating forms and managing user responses through Telegram. \hfill \textbf{2021}
      
      
  
%-------------------------------------------
\end{document}
